Analysis

### 2023-04-24 analysis/analysis.Rmd
Simplify file paths
Removing unnecessary calls to normalizePath and file.path()

```{r}
pollen_locations <- read.csv(file = normalizePath(file.path(here(), "data","raw_data", "pollen_locations.csv")))
pollen_locations
```

@@

```{r}
source(file = normalizePath(file.path(here(), "code", "neotoma_helpers.R")))
```

@@

```{r}
common_names <- read.csv(file = normalizePath(file.path(here(), "data","raw_data", "species.csv")), row.names = 1)
common_names
```

@@

```{r}
ggsave(normalizePath(file.path(here(), "figures","pollenproxy.pdf"), mustWork = F),
       plot = pollenproxy_plot, width = 21, height = 29.7/2, units = "cm")
```

@@

```{r}
c14 <- read.csv(file = normalizePath(file.path(here(), "data","raw_data", "14c_swiss_plateau.csv")))
```

@@

```{r}
sites <- read.csv(file = normalizePath(file.path(here(), "data","raw_data", "site_data_fuzzy.csv")))
```

@@

chrono_rough <- read.csv(file = normalizePath(
  file.path(here(), "data","raw_data", "chrono_rough.csv")
  ),
  row.names = 1)

chrono_vrough <- read.csv(file = normalizePath(
  file.path(here(), "data","raw_data", "chrono_very_rough.csv")
  ),
  row.names = 1)
```

@@

```{r}
lss <- read.csv(file = normalizePath(file.path(here(), "data","raw_data", "dendro_years.csv")))
```

@@

```{r}
write.csv(all_proxies, file = normalizePath(
  file.path(here(), "data","preprocessed_data", "all_proxies.csv"
            ),
  mustWork = F)
  )
```

@@

```{r}
all_proxies <- read.csv(file = normalizePath(
  file.path(here(), "data","preprocessed_data", "all_proxies.csv")
  ),
  row.names = 1)
```

@@

all_proxies_orig <- read.csv(file = normalizePath(file.path(here(), "data","preprocessed_data", "all_proxies.csv")), row.names = 1)

@@

```{r}
PopDens_summary <- this_mcmc_summary[grep("^PopDens", params),]
PopDens_summary$age <- rev(all_proxies_orig$age)
write.csv(PopDens_summary,
          file = normalizePath(
            file.path(here(), "data","preprocessed_data", "popdens_summary.csv"
                      ),
            mustWork = F)
          )
```

@@

```{r}
all_proxies_orig <- read.csv(file = normalizePath(file.path(here(), "data","preprocessed_data", "all_proxies.csv")), row.names = 1)

@@

```{r}
ggsave(normalizePath(file.path(here(), "figures","popdens_estimation.pdf"), mustWork = F),
       plot = popdens_plot_adjusted, width = 21, height = 29.7/2, units = "cm")
```

@@

```{r}
ggsave(normalizePath(file.path(here(), "figures","beta_estimation.pdf"), mustWork = F),
       plot = beta_plot, width = 21, height = 29.7/2, units = "cm")
```
Also interesting is the variation coefficient from the estimation of the Population density:

@@

```{r}
ggsave(normalizePath(file.path(here(), "figures","popvar_plot.pdf"), mustWork = F),
       plot = popvar_plot, width = 21, height = 29.7/2, units = "cm")
```

>>>>

```{r}
pollen_locations <- read.csv(here("data","raw_data", "pollen_locations.csv"))
pollen_locations
```

@@

```{r}
source(here("code", "neotoma_helpers.R"))
```

@@

```{r}
common_names <- read.csv(here("data", "raw_data", "species.csv"), row.names = 1)
common_names
```

@@

```{r}
ggsave(here("figures","pollenproxy.pdf"),
       plot = pollenproxy_plot, width = 21, height = 29.7/2, units = "cm")
```

@@

```{r}
c14 <- read.csv(here("data","raw_data", "14c_swiss_plateau.csv"))
```

@@

```{r}
sites <- read.csv(here("data","raw_data", "site_data_fuzzy.csv"))
```

@@

chrono_rough <- read.csv(here("data","raw_data", "chrono_rough.csv"),
                         row.names = 1)

chrono_vrough <- read.csv(here("data","raw_data", "chrono_very_rough.csv"),
                          row.names = 1)
```

@@

```{r}
lss <- read.csv(here("data","raw_data", "dendro_years.csv"))
```

@@

```{r}
write.csv(all_proxies, here("data","preprocessed_data", "all_proxies.csv"))
```

@@

```{r}
all_proxies <- read.csv(here("data","preprocessed_data", "all_proxies.csv"),
                        row.names = 1)
```

@@

all_proxies_orig <- read.csv(here("data","preprocessed_data", "all_proxies.csv"), row.names = 1)

@@

```{r}
PopDens_summary <- this_mcmc_summary[grep("^PopDens", params),]
PopDens_summary$age <- rev(all_proxies_orig$age)
write.csv(PopDens_summary, 
          here("data", "preprocessed_data", "popdens_summary.csv"))
```

@@

```{r}
all_proxies_orig <- read.csv(here("data","preprocessed_data", "all_proxies.csv"), 
                             row.names = 1)

@@

```{r}
ggsave(here("figures", "popdens_estimation.pdf"),
       plot = popdens_plot_adjusted, 
       width = 21, height = 29.7/2, units = "cm")
```

@@

```{r}
ggsave(here("figures","beta_estimation.pdf"),
       plot = beta_plot, width = 21, height = 29.7/2, units = "cm")
```
Also interesting is the variation coefficient from the estimation of the Population density:

@@

```{r}
ggsave(here("figures","popvar_plot.pdf"),
       plot = popvar_plot, width = 21, height = 29.7/2, units = "cm")
```
